Title Goes Here

### 2020-02-24 paper/paper.tex
Improved wording

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance will be given representation in terms of \ttt{Either}, \ttt{(,)},
\ttt{()} and \ttt{Void}. This "standardized" type representation is
given by \ttt{ERepTy T}. \ttt{ERepTy} is an type family associated to
the type class \ttt{ERep}. This type will be called the \textit{canonical type}
of \ttt{T}.

@@

\ttt{E (ProdMatch x y)} is equivalent to a curried function from \ttt{x} to
\ttt{y} in the expression language .  Note that \ttt{s} will be a (potentially
nested) pair type. For example, \ttt{E (ProdMatch (a, (b, c)) r)} will be
equivalent to \ttt{E (a -> b -> c -> r)}.

>>>>

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given representation in terms of \ttt{Either}, \ttt{(,)},
\ttt{()} and \ttt{Void}. This "standardized" type representation is
given by \ttt{ERepTy T}. \ttt{ERepTy} is an type family associated to
the type class \ttt{ERep}. This type will be called the \textit{canonical type}
of \ttt{T}.

@@

\ttt{E (ProdMatch x y)} is equivalent to a curried function from \ttt{x} to
\ttt{y} in the expression language .  Note that \ttt{s} is a (potentially
nested) pair type. For example, \ttt{E (ProdMatch (a, (b, c)) r)} is
equivalent to \ttt{E (a -> b -> c -> r)}.
